### 2020-04-14 paper/intro.tex

Second, we provide a way for messaging services, like Signal, to use SphinxES 
to relay messages over the devices in \iac{P2P} network with high churn.
We call this the \ac{SPOR} protocol.

>>>>

Second, we provide a protocol, \ac{SPOR}, which optimizes the layers for 
availability.
See \cref{SPOR} for details.
We use a wide definition of churn, a node that is available is online and not 
congested.
This allows systems to relay messages in a \ac{P2P} network with high churn.
For instance, one could convert Signal to use \ac{SPOR} for message delivery.
We use this as the scenario for our performance evaluation.

### 2020-04-14 paper/spor-security.tex

\paragraph*{Node selection}

\sonja{will motivate using the survey/taxonomy}
The onion route provides unlinkability between Alice and Bob as long as the 
message passes at least one honest node on the route.
This means that any adversary, say Eve,  must ensure that the message passes 
through an adversarial node on each layer.
The probability of successful attack is proportional to Eve's size in the 
network, \ie \(f_A = \frac{|D_A|}{|D|}\).
\commentDaniel{Check that we still use the \(D_i\) notation for the devices in 
  \(i\)'s squad.}
If we assume that \(\GetRandomNode\) returns nodes with close to the uniform 
distribution, then the \(\nu w_L\) nodes selected is expected to contain \(f_A 
  \nu w_L\) nodes controlled by Eve.
If \(f_A \nu w_L < \nu\), then Eve is not expected to be present on every layer 
of the route.
Considering how \ac{SPOR} distributed the \(\nu w_L\) selected nodes, Eve's 
best strategy is to have high-availability nodes --- assume that 
\(\avail_{D_E}(t) = 1\) for all Eve's devices \(D_E\).
This way, Eve's devices will be distributed evenly across all layers (provided 
she controls enough of the selected devices).
To succeed, Eve must be chosen in the first layer, the probability of which 
will be \(\frac{f_A}{w_L}\) (for a passive adversary and \(1\) for an active).
If one of her devices is chosen in the first layer, then she can choose one of 
her own devices in the next layer.
If she is present on every layer, she can ensure she relays the message all the 
way to Bob.
In summary, her probability of success is \(\frac{1}{w_L} (1-(1-f_A)^{(w_L-1) 
    \nu +1})\) (or without the \(\frac{1}{w_L}\) factor for an active 
adversary), which can be compared to \((f_A)^\nu\) for classical \ac{OR} (for 
both active and passive adversaries).
\sonja{compare the chance of being present on every
  layer AND chosen in the first layer to regular onion routing where she
  needs to be the (sole) node on each layer. Are we doing
  better/worse/the same?}
\commentDaniel{Hard to say at this time of night \dots}

However, Eve can only be certain that she has relayed the message from Alice to 
Bob if \(\nu = r\), \ie she receives the message from Alice, relays it \(r-1\) 
times and lastly sends it to Bob.
If \(\nu < r\) though, then, due to the indistinguishability and unlinkability 
properties of SphinxES (inherited from \ac{Sphinx}), Eve cannot know for certain if 
Alice is the first node and Bob is the last node. \sonja{but what can
  she learn/guess?}
\commentDaniel{For all she knows there might be another node at either the 
  beginning or the end, she cannot tell.}

Finally, we must point out that the \(\GetRandomNode\) algorithm must be 
privacy preserving.
Consider the following scenario.
Alice requests a set of peers, say \(\{d_1, \dotsc, d_n\}\).
If \(d_i\) interacts in each sampling operation resulting in \(d_i\) being in 
the sample, then \(d_i\) can generate a new public key \(\pk_d^{(j)}\) for each 
sample \(j\).
This means that, if Alice sampled \(d_i\), she knows the public key 
\(\pk_i^{(j)}\), and if \(d_i\) knows it is included in Alice's sample, then it 
will also know a route belongs to Alice whenever \(\pk_i^{(j)}\) is used to 
encrypt the header.
(This follows from the fact that SphinxES is source-routed.)
\Ie every node on Alice's route would know that Alice is either the source or 
the destination.

Although the requirements of the \ac{RPS} being uniformly randomly
distributed and privacy-preserving are not easily met in practice,
there are some promising candidates~\cite[\eg][]{Octopus,BrahmsRPS}.
\name does not put any other constraints on the \ac{RPS} used.

@@

Alice transfers a file \(f\) to Bob during the time interval 
\(\interval{t_0}{t_1}\).
We denote the set of Alice's devices as \(D_A\) and Bob's as \(D_B\).
Bob wants to compute an estimate \(\hat D_A\) which is as close to \(D_A\) as 
possible.

At this point, Bob knows that \emph{at least one} of Alice's devices must have 
been online at any given time in \(\interval{t_0}{t_1}\).
We can also assume that Bob knows all data from the \ac{RPS}, \ie the \((d, 
  \pk_d, \avail_d)\) tuple (see \cref{SPOR}) of \emph{every device that was 
  online at some point during \(\interval{t_0}{t_1}\)}.
Let \(\A_{\interval{t_0}{t_1}}\subseteq \N\times \G^*\times (\RR\to 
  \interval{0}{1})\) denote the set of those tuples.
Thus Bob can approximate \(D_A\) by \(\hat D_A \gets 
  \A_{\interval{t_0}{t_1}}\cap D_B\).

When Alice and Bob interact the next time, either Alice sends a file \(f'\) to 
Bob or Bob sends a file \(f'\) to Alice, then Bob can do the same again:
\(\hat D_A' \gets \A_{\interval{t_0'}{t_1'}} \cap D_B\).
If at least one of \(d, \pk_d, \avail_d\) remains constant, Bob can use that to 
improve his approximation.
Say that \(\avail_d\) remains constant.
Then Bob can improve his approximation to \(\hat D_A \cap_{\avail_d} 
  \hat{D}_A'\), where \(\cap_{\avail_d}\) is the intersection which only 
considers the attribute \(\avail_d\).
Even if \(\avail_d\) is not constant, its variation might stay inside some 
\(\epsilon\)-neighbourhood, and if \(\epsilon\) is small enough, \(\avail_d\) 
might still be used to distinguish Alice.
The same applies for \(d\).
(\(\pk_d\) can be regularly updated.)

With an inaccurate availability function, \(\avail\), this will not be a 
problem as there will be many others (as the system scales) that share the 
same availability distribution.
With more accurate availability estimates we would have to employ techniques 
like \ac{DP} to ensure that Alice's availability distribution is not
(too close to)
unique.

\paragraph*{Robustness}

Stateless routing can result in re-ordered chunks or packets, and
chunks received on different devices of a user's \squad. From \ac{Sphinx},
we inherit unique IDs for each mix packet.
If we provide the mix packets as an ordered list when we communicate them 
out-of-band together with the metadata of the file and they are used in that 
same order, then we can use those IDs to re-order chunks if need be.
The \squad overlay handles intra-squad device 
coordination.
We ensure liveness by acknowledgments and timeouts (as detailed in 
\cref{sec:squad_overlay}), despite the possibility of \squad devices
going offline during transfer or other node or link failures.

\paragraph*{Extended adversary model}%
\label{security-limitations}

A global, passive, network-observing adversary can of course do
statistical disclosure attacks to eventually learn who communicates
with whom~\cite{StatisticalDisclosureAttacks}. There are also denial
of service attacks that can lead to the adversary learning more from
the system~\cite{DenialOfSecurity}.  As mentioned in
\cref{system-model}, we share the adversary model with \ac{Tor}
%and Sphinx
and thus exclude a global passive adversary. Our focus is on
protecting Alice and Bob from each other and from others who also
participate as nodes in the network, not on protecting them from
surveillance. Nevertheless, we offer some reflections on such an
adversary. We hypothesize that our stateless and redundant design
might yield some advantages over classical \ac{OR}. For
example, no control messages are sent back to the source if the
adversary has introduced an error.  \sonja{``But these advantages will
  only postpone the success of the attack, eventually even our
  protocol must resend.'' why?}  \commentDaniel{Due to statistics. We should 
  also look into
  this denial of security.} Another example is that the source-bounded
random-walk and new routes for file chunks make tracking more
difficult than with regular onion routing circuits. A drawback, however, is
that since the chunks can take several paths from source to destination, the source 
will send and the destination will receive more traffic than other nodes in the 
network~\cite{RoutingSurveyAnonymousProtocols}. However, this is mitigated by the fact that the source and 
destination can be several different devices --- \ie from the \squads.

We would also like to point out that the
vulnerability to a global passive attacker is not inherent in Sphinx
or SphinxES, but can be caused by the way they are applied, \ie the
traffic sent. If performance and resource consumption were not an
issue, batched and well-timed message or file transfer by all nodes
would render traffic analysis less efficient. Concretely, \Ac{SPORES} inherits 
the security properties from SphinxES and \ac{SPOR}.
However, both SphinxES and \ac{SPOR} can be used with any mixing strategy, and 
the security they provide is as secure as the mixing strategy (or flushing 
algorithm) allows.
Since \ac{SPORES} is a fully-fledged system, it must make a concrete choice for 
the mixing strategy.
Since \ac{SPORES} aims at low latency, routers do not batch and mix incoming 
messages; they immediately forward any messages.
This puts \ac{SPORES} in the same position as \ac{Tor}, \ie more vulnerable to 
traffic analysis than batching mix-nets~\cite{RoutingSurveyAnonymousProtocols} 
\commentDaniel{we should probably look for the original papers} --- this 
vulnerability is inherited from the mixing strategy.

% \commentDaniel{Predecessor attacks: random walk protocols has the problem that 
%   the adversary can see the initiator (statistically) more often than the other 
%   nodes, and can thus identify the 
%   source~\cite{RoutingSurveyAnonymousProtocols}.
%   Our protocol is a \enquote{bounded} random walk, \ie within limits.}

>>>>

\paragraph*{If Eve is in the layers}

\sonja{will motivate using the survey/taxonomy}
The security of SphinxES rests on the fact that the message must pass at least 
one honest node.
Phrasing it in terms of what the adversary~Eve must accomplish, she must ensure 
that the message passes through an adversarial node.
Now that we have some node selection, we can reason about the likelihood of 
that.

The probability of successful attack is proportional to Eve's size in the 
network, \ie \(q_A = \frac{|\devices_A|}{|\devices|}\).
\commentDaniel{Check that we still use the \(\devices_i\) notation for the 
devices in \(i\)'s squad.}
If we assume that \(\GetNode\) returns nodes with close to the uniform 
distribution, then the \(\nu w_L\) nodes selected is expected to contain \(q_A 
\nu w_L\) nodes controlled by Eve.
If \(q_A \nu w_L < \nu\), then Eve is not expected to be present on every layer 
of the route.

Considering how \ac{SPOR} distributed the \(\nu w_L\) selected nodes, Eve's 
best strategy is to have high-availability nodes --- assume that 
\(\avail[\devices_E] = 1\) for all Eve's devices \(\devices_E\).
This way, Eve's devices will be distributed evenly across all layers (provided 
she controls enough of the selected devices).

To link Alice and Bob, Eve must be chosen in the first layer and the route must 
contain the maximum number of layers~\(r\).
(Remember, we chose \(\nu+1\leq r\) in \cref{SphinxEScreate}.)
The probability for Eve to be chosen in the first layer will be 
\(\frac{q_A}{w_L}\) (for a passive adversary and \(1\) for an active).
If one of her devices is chosen in the first layer, then she can choose one of 
her own devices in the next layer.
If she is present on every layer, she can ensure she relays the message all the 
way to Bob.
In summary, her probability of success is \(
  \frac{1}{w_L} (1-(1-q_A)^{(w_L-1) \nu +1})
\) (or without the \(\frac{1}{w_L}\) factor for an active adversary), which can 
be compared to \((q_A)^\nu\) for classical \ac{OR} (for both active and passive 
adversaries).

However, Eve can only be certain that she has relayed the message from Alice to 
Bob if \(\nu+1 = r\), \ie she receives the message from Alice, relays it 
\(r-1\) times and lastly sends it to Bob.
If \(\nu+1 = r-1\), then Eve learns that either Alice must be the sender or Bob 
must be the recipient.
(This is due to the indistinguishability and unlinkability properties of the 
ideal functionality.)
If \(\nu+1 \leq r-2\), then Eve cannot certainly tell whether Alice and Bob are 
end points of simply honest relays for someone else.

That reasoning is only valid when there is more than one node in a layer.
If Eve learns that there is only one node in the next layer, it is likely the 
recipient node.

\paragraph*{Privacy of \(\GetNode\)}

The \(\GetNode\) algorithm must be privacy preserving.
Consider the following scenario.
Alice requests a set of peers, say \(\{d_0, \dotsc, d_{n-1}\}\).
If \(d_i\) interacts in each sampling operation resulting in \(d_i\) being in 
the sample, then \(d_i\) can generate a new public key \(\pk_d^{(j)}\) for each 
sample \(j\).
This means that, if Alice sampled \(d_i\), she knows the public key 
\(\pk_i^{(j)}\), and if \(d_i\) knows it is included in Alice's sample, then it 
will also know a route belongs to Alice whenever \(\pk_i^{(j)}\) is used to 
encrypt the header.
(This follows from the fact that the ideal functionality is source-routed.)
\Ie every node on Alice's route would know that Alice is either the source 
(forward header) or the destination (reply header).

\paragraph*{Distributions in layers}

The output of Alice's query to \(\GetNode\) must only be learned by Alice.
Again, Alice requests a set of peers~\(\{d_0, \dotsc, d_{\nu w_L}\}\).
Say that Eve observes all of Alice's requests.
Now, both Alice and Eve can compute the output of \(\CreateLayers\) 
(deterministic).
Now, if Eve is on that path, say in layer~\(L_i\), she can recognize Alice's 
onions by the composition of the next layer~\(L_{i+1}\).
The likelihood that Bob has a layer \(L_j = L_{i+1}\) is small.
Consider normal onion routing, there the probability that Alice and Bob both 
chose node \(N\) is \(\frac{1}{|\devices|}\).
Here, however, it is \((\frac{1}{|\devices|})^{w_L}\), for large sets of 
devices~\(\devices\).

Consider a node controlled by Eve.
Given the low probability of \(\frac{1}{|\devices|^{w_L}}\) that a combination 
of nodes appear as a layer, the combination Alice's own devices in the final 
layer will have a higher probability of appearing.
Thus, any more frequently appearing combination of nodes is with high 
likelihood the recipient devices of a user.
(This is all the more true when there is only one device in a layer.)

@@

Alice sends the message \(m\) to Bob during the time interval 
\(\interval{t_0}{t_1}\).
We denote the set of Alice's devices as \(\devices_A\) and Bob's as 
\(\devices_B\).
Bob wants to compute an estimate \(\hat \devices_A\) which is as close to 
\(\devices_A\) as possible.

At this point, Bob knows that \emph{at least one} of Alice's devices must have 
been online at any given time in \(\interval{t_0}{t_1}\).
We can also assume that Bob knows all data from the \ac{RPS}, \ie the \((d, 
\pk_d, a_d)\) tuple (see \cref{SPOR}) of \emph{every device~\(d\) that was 
online at some point during \(\interval{t_0}{t_1}\)}.
Let \(\A_{\interval{t_0}{t_1}}\subseteq \N\times \G^*\times \interval{0}{1}\) 
denote the set of those tuples.
Thus Bob can approximate \(\devices_A\) by \(\hat \devices_A \gets 
\A_{\interval{t_0}{t_1}}\cap \devices_B\).

When Alice and Bob interact the next time, either Alice sends a message \(m'\) 
to Bob or Bob sends a file \(m'\) to Alice, then Bob can do the same again:
\(\hat \devices_A' \gets \A_{\interval{t_0'}{t_1'}} \cap \devices_B\).
If at least one of \(d, \pk_d, a_d\) remains constant, Bob can use that to 
improve his approximation.
Say that \(a_d\) remains constant.
Then Bob can improve his approximation to \(
  \hat \devices_A \cap_{a_d} \hat \devices_A',
\) where \(\cap_{a_d}\) is the intersection which only considers the attribute 
\(a_d\).
Even if \(a_d\) is not constant, its variation might stay inside some 
\(\epsilon\)-neighbourhood, and if \(\epsilon\) is small enough, \(a_d\) might 
still be used to distinguish Alice.
The same applies for \(d\) and \(\pk_d\).

With an inaccurate availability function~\(\avail\) (\eg \(k\)-anonymous, as 
mentioned above) this will not be a problem as there will be many others (as 
the system scales) that share the same availability distribution.
The public key~\(\pk\) can be refreshed regularly.
The main problem is any persistent identifier (address) \(d\).

### 2020-04-14 paper/spores.tex

%!TEX root = spores.tex

\section{Design of the \name file transfer system}%
\label{design}

% \sonja{will frame and structure (A) squad overlay (prediction) (B)
%   global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
%   general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
%   if not included earlier (F) out-of-band}
% \commentDaniel{I suggest the following structure:
%   (A) SphinxES
%   (B) SPOR (global overlay)
%   (C) SPORES (local overlay).
%   My original idea was to make SphinxES its own section before the design 
%   section instead of a subsection in the design section.}

%\include*{spor}
%\include*{squad-overlay-design}
\include*{file-transfer-design}

>>>>

\section{\Acf*{SPORES}}%
\label{SPORES}%

We will now extend \ac{SPOR} into \ac{SPORES}.
It is becoming more and more common that people own more than one online device 
(\eg a laptop and a smartphone).
We will utilize this in the construction of \ac{SPORES}.
Thus \ac{SPORES} is different in two aspects:
First, the recipient layer consists of several devices instead of only one.
These devices, the e-squad of Bob, will then coordinate to ensure the relevant 
device gets the message.
We assume there is a protocol which solves this problem.
For instance, \textcite{luxey:cascade} introduce a protocol that allows the 
devices of an e-squad to coordinate user sessions in the face of churn.

Second, we will introduce how to do fragmentation and reassembly for large 
messages.
Consider that the message \(m\) that Alice wants to send to Bob is too large to 
successfully pass every layer of the route.
\Eg each device goes offline and back online every \(t\) seconds, the bandwidth 
is \(w\) bits per second and the message is \(|m|\) bits; if \(|m| > t w\), 
then the message \(m\) can never be delivered as any device will go offline 
before relaying it to the next node.
The natural solution is to split \(m\) into \(n\) parts, \(m_0, \dotsc, 
  m_{n-1}\), where \(|m|/n\leq t w\).
The problem now is that \(m_i\) and \(m_j\) (\(i\neq j\)) might end up on 
different devices.
But that problem is solved by the protocol mentioned above.
This allows us to send large messages, such as videos, more efficiently.

The parameters \(t\) and \(w\) must be empirically approximated and used as 
global configuration parameters for the system.
We run simulations for various values of \(t\) and \(w\) in \cref{Performance}.
In this section we describe a file-transfer protocol for splitting a large 
message, sending the fragments using \ac{SPOR} and reassemble them --- even if 
the fragments are received by different devices of the squad.

\subsection{Fragmentation and reassembly}%
\label{sec:file_transfer}

Alice wants to send the message \(m\) to Bob, \(m\) is \(|m|\) bits long.
Bob creates a reply header and gives it to Alice.
Alice splits \(m\) into \(n\) parts \(m_0, \dotsc, m_{n-1}\).
Alice sends \(|m|\), \(n\), \(\hash(m)\), \(\hash(m_0), \dotsc, 
\hash(m_{n-1})\) to Bob using \ac{SPOR} and Bob's reply header.
(Remember, this means that Bob receives a reply header with the data, so that 
he can later reply to Alice.)

Bob runs \(\CreateReply\) \(n\) times, the node sets passed to \(\CreateReply\) 
are created as in \cref{SPOR}, but all of Bob's devices populate the recipient 
set.
Bob notes the order of the identifiers, \(I\), of each header and sends the 
headers in that order to Alice (using Alice's reply header).

Alice receives the headers and keeps the order of the headers.
For each \(0\leq i < n\), she uses \(\UseReply\) with \(m_i\) as payload to get 
a header \(\hat M_i\).
Then she constructs the final header \(M_i\) by running \(\CreateFwd\) with 
\(\hat M_i\) as payload and the final layer set to \(\{\rdvnode\}\) (to 
indicate to the last node that it is a rendezvous node).
She then sends \(M_i\) along the route.
We note that Alice can process all pieces in parallel as long as she uses the 
headers she got from Bob in the correct order --- \ie \(M_i\) contains \(m_i\) 
as payload.

When the headers are used in the correct order Bob can use the identifiers from 
the headers (\(I\)) to correctly reassemble the fragments despite out-of-order 
delivery.

As above, each payload also contains a reply header for Bob, these can be used 
by Bob to inform Alice at regular time intervals about which chunks have been 
received and which are missing.

%\commentDaniel{I leave the remaining details for someone else to write up.
 % What we need is the details of how Bob's devices syncs and reassembles files.
 % Maybe this is reduced to Sprinkler or something.}
